### 2022-04-26 LaTeX_Plos/ResponseToReviewers.tex

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
%\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\commentAnthony}[2][1=]{\todo[linecolor=red,backgroundcolor=blue!25,bordercolor=red,#1]{#2}}

@@

\textbf{Comments:} 
1. Uniform distribution of silver on the PET fabrics is crucial to the good antiviral property. How did the authors adjust silver distribution via drop casting method? How about the silver content on the coating? Cytotoxicity is needed to characterize the coated PET fabrics.

\blue{PET samples were dampened with alcohol to improve the spreading of the silver coatings during drop casting. The silver content of the coating has been added in the Materials and Methods section. Cytotoxicity assessment is outside the scope of the work.  Line 253 in the Conclusion has been updated to state, ``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
commercial use."}

2. The authors need to characterize PDMS coatings, for example, the thickness of PDMS coating? How did reactive silver ink and silver nanoparticle influence the final morphology of PDMS coatings?

\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS
coating appears roughened due to the underlying morphology of the silver nanoparticles
or silver ink coated fabrics." }
\commentPaul{Anything about thickness?}
\commentAnthony{I do not have exact measurements. I have some pictures but they are low quality. We could say less than 1 micron. }

@@

4. Other properties - technical textiles don't just need to exhibit their desired primary benefit (in this case antiviral); does the treatment compromise any other aspects of textile properties that could be relevant to its use such as flexibility and comfort in wear?

\blue{We appreciate the suggestion and are considering analysis of flexibility and comfort 
in future work.}
%\blue{Future work may consider other textile properties and this limitation is acknowledged.  }

Finally, the descriptions of materials in the Materials and Methods are too vague and this prevents the work from being easily duplicated. Trademarks such as Antocon(R) are not acknowledged which is a product brand name not a supplier. That range of wipes contains more than one PET knit wipe so the specific one used should be described. The specific bleach is not given, only that it was purchased from Giant Eagle - was it Clorox(R) or their own brand? Do they really only sell one? Could product codes be provided for other purchases from Sigma-Aldrich unless they really only sell one PBS, FBS and PDMS product?

\blue{The supplier has been added, as well as a better description of the materials and methods. The specific bleach is Giant Eagle brand and (Giant Eagle brand, SKU: 00030034936150) has been added to the text. 
%\commentPaul{Perhaps better description of this bleach.  Concentration level.  Sodium hypochlorite concentration level}
A better description of the other materials that were used have been changed in the Materials and Methods section. Product numbers for PBS (P5493) and FBS (12103C) has been added to the text. PDMS (Sylgard 184) has been added to the text. 
%\commentPaul{Try to provide better description of materials even if there is only one.  Sometimes, companies will change how many they sell or change the composition of the one product they sell.}
}

@@

101 The x-axis of the XRD pattern should change to (2$\theta$ (°)). Please at Y-axis please remove numbers if it is going to be reported by Arbitrary unit or remove (a.u.).

\blue{The axes have been changed. }

104 Author mentioned that the untreated PET is fully wetted by water and Fig 2 (a) shows that the water static, contact angle, for PET is zero. Although other studies such as the Indian Journal of Fibre \& Textile Research Vol. 37, September 2012, pp. 287-291 showed the water contact angle of untreated PET fabric is 124.24$\degree$.

\blue{The paper mentioned uses weaved PET fabric which may be more repellent. The PET we used is knit and is fabricated to have high sorbency. }
\commentPaul{See above comment about PET having lower surface energy than other textiles. Perhaps, this PET is not so low surface energy?}  
\commentAnthony{Maybe. I think the reviewer just forgot to add with PDMS to make a low surface energy surface. We never say PET itself is low surface energy.}

### 2022-04-26 LaTeX_Plos/PlosOne.tex
Anthony's changes

\section*{Materials and Methods}
%\subsection{Sample Preparation}
Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.  PBS, FBS, PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich. Reactive silver inks (720 series, approx. 20\% silver) was provided by Electroninks. Silver nanoparticles (20 nm, 1 mg/mL in sodium citrate) were purchased from NanoComposix. Household bleach (Giant Eagle brand) was purchased from Giant Eagle. Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb. Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C. Virus stocks in PBS were prepared with A549 human lung carcinoma cells. The virus stocks were diluted in sterile PBS to the experimental titers used.

>>>>

\section*{Materials and Methods}
%\subsection{Sample Preparation}
Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.  PBS (P5493), FBS (12103C), PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich. Reactive silver inks (720 series, approx. 20\% silver) was provided by Electroninks. Silver nanoparticles (20 nm, 1 mg/mL in sodium citrate) were purchased from NanoComposix. Household bleach (Giant Eagle brand, SKU: 00030034936150) was purchased from Giant Eagle. Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb. Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C. Virus stocks in PBS were prepared with A549 human lung carcinoma cells. The virus stocks were diluted in sterile PBS to the experimental titers used.
